\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-19 notes/2loopNLSM.tex
more edits to intro
intro done. now going to add citations

\setstackgap{S}{6pt}
\setstackgap{L}{7pt}
\newpage
\section{Introduction}\label{intro}
Since the turn of the century, our understanding of the $S$-matrix and its hidden structure has expanded dramatically. At the heart of this progress is the mantra that physical observables are simpler when studied on-shell. However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell structure at the heart of many quantum field theories. A shining example of this hidden structure is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors. When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{}.

However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, the duality between color and kinematics remains a conjecture at loop level. Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{}. In this work, we use the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven to permit color-dual representations at tree-level \cite{}, as case studies for advancing our understanding of the kinematic algebra to the multi-loop level.

We begin by providing background on the duality between color

In contrast to presently available on two-loop construction of color-dual integrands \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional. This makes our methods and results particularly well suited or tackling  We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public. 
 \section{Background}\label{background}
To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions. We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM. 
\subsection{Color-dual Amplitudes}\label{onShellCK}

>>>>

\setstackgap{S}{6pt}
\setstackgap{L}{7pt}
\newpage
\section{Introduction}\label{intro}
Since the turn of the century, our understanding of the $S$-matrix and its hidden structures has expanded dramatically. At the heart of this progress is the mantra that physical observables are simpler when studied on-shell. However, while plugging in on-shell states certainly offers a path towards taming the factorial growth of Feynman diagrams, it also obscures the off-shell structure at the heart of many quantum field theories. A shining example of this hidden simplicity is the duality between color and kinematics \cite{BCJ}, which states that the kinematic numerators of gauge theory amplitudes can be rearranged to obey the same algebraic identities as the constituent color factors. When this duality is realized globally off-shell, it dramatically decreases the combinatorial complexity posed by integrand construction, and offers a path towards efficient assembly of quantum gravity integrands directly from simpler gauge theory building blocks via the double copy \cite{}.

However, despite the tremendous success in leveraging this duality to compute gauge and gravity observables to high orders in perturbation theory \cite{}, the color-kinematics remains a conjecture at loop level. Indeed, there are many examples in the literature where identifying color-dual representations beyond one-loop has posed a formidable challenge \cite{}. In this work, we use the nonlinear sigma model (NLSM) and Yang-Mills, two theories proven to permit color-dual representations at tree-level \cite{}, as case studies for advancing our understanding of the kinematic algebra to the multi-loop level.

We begin with an overview of color-kinematics duality in \cref{background}. We then construct a manifestly color-dual theory in \cref{sec:cubic}, which generates $D$-dimensional color-dual $n$-point numerators for both NLSM and the self-dual sector of Yang-Mills through one-loop. The construction of this theory, which we dub semi-abelian Yang-Mills, relies on isolating the cubic sector of pure Yang-Mills amplitudes from the four-point contacts that are needed to fully realize non-abelian gauge symmetry. Promoting this construction beyond one-loop runs into an obstruction that we describe in \cref{2loopObstruction}.

Faced with this obstruction, we study the multi-loop sector of both NLSM and Yang-Mills in \cref{2loopBoot} using an ansatz based color-dual bootstrap. In contrast to presently available on two-loop construction of color-dual integrands \cite{}, our results are completely agnostic to the spacetime dimension; all the polarizations and momenta appearing in our construction will remain formally $D$-dimensional. This makes our methods and results particularly well suited for algorithmically extracting rational terms from the $D$-dependence of dimensionally regulated loop momenta. We are able to achieve this by employing a custom solver, \texttt{FiniteFieldSolve}, which will soon be made public.

With this solver, we are able to compute a two-loop integrand for NLSM that globally manifests the duality off-shell. This represents a new bench mark for color-dual representations in non-supersymmetric gauge theories. However in contrast, we find surprisingly that Yang-Mills does not permit a globally color-dual representation when considering the most general polynomial ansatz of irreducible scalar products. Concretely, we find a sharp failure point between the ``kissing triangles'' cut, and the following jacobi triple:
\begin{equation}
   \NMCutC
  \Rightarrow
  \JacobiOneDoubleBox +  \JacobiOneCrossedBox + \JacobiOnePentaTriangle \neq 0 \,.
\end{equation}
We comment on the implications of this finding in \cref{conclusions}, and discuss alternative approaches where one relaxes field theoretic locality in order to accommodate the construction of globally color-dual numerators to all-loop order.

\section{Background}\label{background}
To set the stage, in this section we provide an overview of color-kinematics duality -- both the on-shell and off-shell constructions. We then explicate our approach for constructing color-dual integrands in theories for which the off-shell kinematic algebra has not yet been identified, like Yang-Mills and NLSM. 
\subsection{Color-dual Amplitudes}\label{onShellCK}
